Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}

### 2019-04-15 manuscript.Rnw
almost done with revision

Yet, just as analysis of full sample conjoint data is often descriptive in nature, it is also the case that conjoint analysts frequently interpret differences in conditional AMCEs descriptively rather than causally. For example, in one analysis \citet{HainmuellerHopkinsYamamoto2014} visually compare the pattern of AMCEs among high- and low-ethnocentrism respondents and interpret that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' (22). \citet{BallardRosaMartinScheve2016} make similar comparisons in their tax policy conjoint: ``While there are few strong differences in preferences for taxing the lower three income groups (the `hard work' group has slightly lower elasticities for taxing the poor), there are strong differences in preferences for taxing the rich'' (12). In \citet{BechtelScheve2013} conjoint on support for international climate change agreements in the United States, United Kingdom, Germany, and France, they summarize their results as ``We find that individuals in all four countries largely agree on which dimensions are important and to what extent'' (13765). In these examples, the differences between conditional AMCEs are used as a way of descriptively characterizing differences in \textit{preferences} (i.e. levels of support) between the groups rather than differences in \textit{causal effects on preferences} in the groups.

@@

It is worth highlighting two further features in Figure \ref{fig:bechtel_difference_comparison}. First, the alternative differences-in-AMCEs estimates vary mechanically around the difference in marginal means, as the reference category varies. The difference between marginal means for two groups are always fixed in the data, so the differencing of subgroup AMCEs is merely an exercise is centering those differences at arbitrary points along the range of observed differences in marginal means. Differences-in-AMCEs for a given feature level must therefore necessarily sometimes be positive and sometimes be negative, depending on the reference category used in estimating them. The direction of the difference per se conveys no information about underlying pattern of preferences in the two groups.

Second, and more practically, because there is no category for which the preferences of the two subgroups in this example are identical, no choice of reference category would have led to inferences from differences-in-AMCEs that accurately reflect the underlying difference in preferences. Even in the 84 Euro per month level, the difference between the two groups is slightly positive. Were there a category for which subgroup preferences were exactly equal, then we could choose that as the reference category and interpret differences-in-AMCEs as differences in preferences. But there is never any guarantee that such a reference category exists. If multiple subgroup analyses are performed, it is unlikely the same reference category would work well across all analyses, making consistent interpretation difficult. And because conjoint analysis generates a sparse feature matrix (where many combinations of feature levels are unobserved in the data), it is rarely possible to empirically select an appropriate set of reference categories using the observed data. It is impossible to know which cell --- of the tens of thousands in the design --- is the best choice of reference. Indeed it is possible that there is no such cell for which preferences are identical in the two groups; such a cell may exist, but there is no reason to expect that it should exist in any given application or that it would happen to be observed. Thus, there is no way to use conditional AMCEs or differences between those conditional AMCEs to convey the underlying similarity or differences in preferences across sample subgroups.

@@

Researchers and consumers of conjoints can avoid the inferential errors that accompany conditional AMCEs by focusing attention on (subgroup) marginal means, differences between subgroup marginal means to infer subgroup differences in preferences toward particular features, and omnibus nested model comparisons to infer subgroup differences across many features. To demonstrate each of these three techniques we provide a complete example based upon \citeauthor{HainmuellerHopkinsYamamoto2014}'s analysis of their immigration conjoint by respondent enthnocentrism, which finds that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' \citep[22]{HainmuellerHopkinsYamamoto2014}. First, we show how different reference categories could have led to distinctly different conditional AMCEs and, therefore, interpretations of subgroup preference similarity. Second, we show how differences in marginal means clearly convey the similarity of these two subgroups without any sensitivity to reference category. Finally, we show how tested model comparisons would have provided \citeauthor{HainmuellerHopkinsYamamoto2014} with a statistic test of the claimed similarity in levels of support between these two respondent subgroups.

@@

<<hainmueller_subgroup_example_plot, dependson=c("data_hainmueller_immigration", "hainmueller_subgroup_example"), fig.width=8, fig.height=6, fig.cap="Comparison of AMCEs for Low- and High-Ethnocentrism Respondents Using Two Alternative Reference Categories Choices for Hainmueller et al. (2014) Immigration Experiment", message=FALSE>>=
plot(
  subset(
    amce_ref_example_merged,
    feature %in% c("Education", "CountryOfOrigin", "Job")
  ),
  group = "ethnocentrism_split", 
  feature_headers = FALSE, 
  legend_title = "Ethnocentrism", 
  vline = 0
) + 
  scale_colour_manual(
    "Ethnocentrism", limits = c("high", "low"), values = c("Red", "Blue")
  ) +
  facet_grid(
    rows = vars(feature), 
    cols = vars(dataset), 
    scales = "free_y", 
    space = "free_y", 
    labeller = function(x) label_value(x, multi_line = FALSE)
  ) +
  theme(
    strip.background = element_rect(fill="white", colour="white"),
    strip.text.x = element_text(size = 8),
    strip.text.y = element_blank()
  )
@

To begin, consider the left and right facets of Figure \ref{fig:hainmueller_subgroup_example_plot}, which shows estimated subgroup AMCEs for three features from the immigration study. In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in levels of support between the two subgroups. In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.

@@

<<hainmueller_mm_diffs, dependson=c("data_hainmueller_immigration"), fig.height = 5, fig.width=8, fig.cap="Differences in Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment", message=FALSE>>=
mm_by_ethnocentrism <- cj(
  subset(hainmueller_immigration, !is.na(ethnocentrism_split)),
  ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry,
  id = ~ CaseID,
  estimate = "mm_diff",
  by = ~ ethnocentrism_split
)
plot(
  subset(
    mm_by_ethnocentrism,
    feature %in% c("Country of Origin", "Job", "Education")
  ), 
  vline = 0, 
  xlim = c(-0.3,0.3), 
  xlab = "Estimated Difference in Marginal Means"
) +
  scale_colour_manual("feature", values = rep("Black", 9)) +
  ggplot2::theme(legend.position = "none")
@

@@

<<hainmueller_language_diffs, dependson=c("data_hainmueller_immigration"), eval=TRUE, echo=FALSE>>=
hainmueller_anova_language <- cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ LanguageSkills, id = ~ CaseID, by = ~ ethnocentrism_split)
@

For the \citeauthor{HainmuellerHopkinsYamamoto2014} language feature, the resulting F-test for the model comparison in this case again gives us little reason to believe there are subgroup differences: \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_language$Df[2], hainmueller_anova_language[["Resid. Df"]][1], hainmueller_anova_language$F[2], hainmueller_anova_language$"Pr(>F)"[2])}. We could repeat such pairwise comparisons or omnibus comparisons for each feature in the design.

Furthermore, we could also directly visualize differences in conditional marginal means for this feature --- and all features --- as in Figure \ref{fig:hainmueller_mm_diffs}. This provides a more direct presentation of \textit{differences} between subgroup preferences as the vertical line indicates feature levels for which there is no difference between the two groups. Positive values to the right of the line indicate positive differences (high ethnocentrism respondents are more favorable toward immigrants with this feature than low ethnocentrism respondents) and negative value to the left of zero convey the opposite. A further advantage of this plot is that unlike displays of conditional AMCEs, differences in conditional marginal means communicate subgroup differences for all feature levels including the reference categories. This display makes readily clear what was only indirectly apparent in Figure \ref{fig:hainmueller_mm_diffs}: there are indeed no sizeable and only a few statistically apparent differences in preferences between the two groups.

<<hainmueller_all_diffs, dependson=c("data_hainmueller_immigration"), eval=TRUE, echo=FALSE>>=
hainmueller_anova_all <- cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ Gender + Job*Education + LanguageSkills + CountryOfOrigin*ReasonForApplication + JobExperience + JobPlans + PriorEntry, id = ~ CaseID, by = ~ ethnocentrism_split)
@

@@

As before, we can perform an omnibus tests for the presence of any subgroup differences across all features, again using nested model comparison of two equations: (a) one estimating only effects of the features, and (b) the same model with additional interactions between the subgrouping covariate and all features. The result of that test for differences by ethnocentrism from the immigration experiment is: \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_all$Df[2], hainmueller_anova_all[["Resid. Df"]][1], hainmueller_anova_all$F[2], hainmueller_anova_all$"Pr(>F)"[2])}, which further demonstrates that the substantive interpretation provided by \citet{HainmuellerHopkinsYamamoto2014} accurately identified a lack of between-group differences.

This kind of nested model comparison test can also be used to assess heterogeneity across conjoint features \citep[see also][]{EgamiImai2018}. For example, \citet{TeeleKallaRosenbluth2018} report just such a test for how effects of features other than candidate sex may differ between male and female candidates, finding no such heterogeneity (8--9). Fortunately, the original analysis accurately detected an absence of subgroup differences, yet a subtly different set of analytic decisions about reference categories (as shown in Figure \ref{fig:hainmueller_subgroup_example_plot}) could have led to a quite different conclusion. As an example, \citet{BechtelScheve2013} argue that their conjoint results show ``individuals in all four countries largely agree on which dimensions are important and to what extent'' \citep[13765]{BechtelScheve2013}, but a nested model comparison shows the countries do differ in their preferences \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", bechtel_anova_country$Df[2], bechtel_anova_country[["Resid. Df"]][1], bechtel_anova_country$F[2], bechtel_anova_country$"Pr(>F)"[2])}. This cross-country variation largely driven by differences in sensitivity to monthly household costs feature, \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", bechtel_anova_country_cost$Df[2], bechtel_anova_country_cost[["Resid. Df"]][1], bechtel_anova_country_cost$F[2], bechtel_anova_country_cost$"Pr(>F)"[2])}, with the United Kingdom and United States being more cost sensitive than Germany and France. Visual comparisons of conditional AMCEs can sometimes provide accurate insights into subgroup differences in preferences, but ulimately there is no guarantee that they do in any particular analysis.

@@

This article has identified several challenges related to the analysis and reporting of conjoint experimental designs, particularly analyses of subgroup differences. We suggest that conjoint analyses should report not only average marginal component effects (AMCEs) but also descriptive quantities that better convey underlying preferences over profile features and better convey subgroup differences in those preferences. Marginal means contain all of the information provided by AMCEs and more. Consequently, our intention here is not to substantively undermine any previous set of results, but instead to urge researchers moving forward to demonstrate considerable caution in how they design, analyze, and present the results of these types of descriptive experiments. We have relatively straightforward and hopefully uncontroversial advice for how analysts of conjoint experiments should proceed:

@@

The popularity of conjoint analyses in recent years highlights the power of the design and the important contributions made by \citet{HainmuellerHopkinsYamamoto2014} in providing a novel causal interpretation of these fully randomized factorial designs. Yet with new tools always come new challenges. The now-common practice of descriptively interpreting conjoints requires more caution than is immediately obvious. This paper has demonstrated several such challenges and hopefully provides useful advice for how researchers should proceed with the analysis of such designs.

To facilitate such analysis and, especially, to provide easy-to-use tools for calculating marginal means and performing reference category selection diagnostics, we provide software called \textbf{cregg} \citep{Leeper2018cregg} available from the Comprehensive R Archive Network; this manuscript is written as a reproducible knitr document \citep{Xie2015} that contains complete code examples that will perform all analyses and visualization used throughout this article. With that resource in-hand, researchers should be well-equipped to analyze conjoint designs without running into the analytic challenges discussed here.

@@

<<hainmueller_immigration_amce_appendix, dependson=c("data_hainmueller_immigration"), fig.height=8, fig.width=8>>=
p1 <- plot(
  cregg::cj(
     hainmueller_immigration, 
     ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry + Education:Job + CountryOfOrigin:ReasonForApplication,
     id = ~ CaseID
  ), vline = 0
) + 
  ggplot2::scale_x_continuous(
    limits = c(-0.4, 0.4), 
    breaks = c(-0.4, -0.3, -0.2, -0.1, 0.0, 0.1, 0.2, 0.3, 0.4)
  ) + 
  ggplot2::geom_text(
    aes(label = ifelse(is.na(std.error), "", sprintf("%0.2f (%0.2f)", estimate, std.error))),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
 ) + 
 theme(legend.position="none")
p2 <- plot(
  cregg::cj(
     hainmueller_immigration, 
     ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry,
     id = ~ CaseID,
     estimate = "mm"
  ), vline = 0.5
) + 
  ggplot2::scale_x_continuous(
    limits = c(0.1, 0.9), 
    breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
  ) + 
  ggplot2::geom_text(
    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
  ) + 
  theme(legend.position="none")
#gridExtra::grid.arrange(p1, p2, ncol=2)
p1
p2
@

<<hainmueller_immigration_amce_appendix_split, dependson=c("data_hainmueller_immigration"), fig.height=4, fig.width=8>>=
plot(
  rbind(
    within(cj(
      subset(hainmueller_immigration, constraint1constrained), 
      ChosenImmigrant ~ CountryOfOrigin + ReasonForApplication,
      id = ~ CaseID,
      estimate = "mm"
    ), Constraint <- "Constrained"),
    within(cj(
      subset(hainmueller_immigration, constraint1unconstrained), 
      ChosenImmigrant ~ CountryOfOrigin + ReasonForApplication,
      id = ~ CaseID,
      estimate = "mm"
    ), Constraint <- "Unconstrained")
  ), vline = 0.5
) + facet_wrap(~Constraint)

plot(
  rbind(
    within(cj(
      subset(hainmueller_immigration, constraint2constrained), 
      ChosenImmigrant ~ Job + Education,
      id = ~ CaseID,
      estimate = "mm"
    ), Constraint <- "Constrained"),
    within(cj(
      subset(hainmueller_immigration, constraint2unconstrained), 
      ChosenImmigrant ~ Job + Education,
      id = ~ CaseID,
      estimate = "mm"
    ), Constraint <- "Unconstrained")
  ), vline = 0.5
) + facet_wrap(~Constraint)
@

@@

@@

<<tkr_subgroup_example_plot, dependson=c("data_tkr", "tkr_subgroup_example"), fig.width=10, fig.height=10, fig.caption="Alternative Reference Categories Features in Teele et al. (2018) Candidate Experiment">>=
plot(amce_ref_tkr_merged, group = "PartyID", feature_headers = FALSE, legend_title = "Party Identification", vline = 0) + 
  facet_grid(rows = vars(feature), cols = vars(dataset), scales = "free_y", space = "free_y", labeller = function(x) label_value(x, multi_line = FALSE)) +
  theme(strip.text.x = element_text(size = 8),
        strip.text.y = element_text(size = 5))
@

@@

@@

@@

@@

@@

<<bechtel_reciprocity_reference>>=
# ``Individuals who pretreatment exhibit reciprocal behavior [...] are almost twice as sensitive to both the number of countries participating and the proportion of emissions represented than individuals who do not'' (13768). This sensitivity is accurately stated but the use of conditional AMCEs implies that the subgroup difference is due to differences in favorability toward agreements involving 20 countries and differing opinions over agreements with 80 or 160 countries, while in reality the differences lie in 20-country and 160-country agreements and the groups do not differ in their favorability toward 80-country agreements at all. 
plot(cj(bechtel, choice_cj ~ ctries_cj + emissions_cj, weights = ~ weight, id = ~ ID, estimate = "mm", by = ~ reciprocity), group = "BY", vline = 0.5)
@

>>>>

Yet, just as analysis of full sample conjoint data is often descriptive in nature, it is also the case that conjoint analysts frequently interpret differences in conditional AMCEs descriptively rather than causally. For example, in one analysis \citet{HainmuellerHopkinsYamamoto2014} visually compare the pattern of AMCEs among high- and low-ethnocentrism respondents and interpret that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' (22). \citet{BallardRosaMartinScheve2016} make similar comparisons in their tax policy conjoint: ``While there are few strong differences in preferences for taxing the lower three income groups (the `hard work' group has slightly lower elasticities for taxing the poor), there are strong differences in preferences for taxing the rich'' (12). In the \citet{BechtelScheve2013} conjoint on support for international climate change agreements in the United States, United Kingdom, Germany, and France, they summarize their results as ``We find that individuals in all four countries largely agree on which dimensions are important and to what extent'' (13765). In these examples, the differences between conditional AMCEs are used as a way of descriptively characterizing differences in \textit{preferences} (i.e. levels of support) between the groups rather than differences in \textit{causal effects on preferences} in the groups.

@@

It is worth highlighting two further features in Figure \ref{fig:bechtel_difference_comparison}. First, the alternative differences-in-AMCEs estimates vary mechanically around the difference in marginal means, as the reference category varies. The difference between marginal means for two groups are always fixed in the data, so the differencing of subgroup AMCEs is merely an exercise is centering those differences at arbitrary points along the range of observed differences in marginal means. Second, and more practically, because there is no category for which the preferences of the two subgroups in this example are identical, no choice of reference category would have led to inferences from differences-in-AMCEs that accurately reflect the underlying difference in preferences. Even in the 84 Euro per month level, the difference between the two groups is slightly positive. Were there a category for which subgroup preferences were exactly equal, then we could choose that as the reference category and interpret differences-in-AMCEs as differences in preferences. But there is never any guarantee that such a reference category exists. Thus, there is no way to use conditional AMCEs or differences between those conditional AMCEs to convey the underlying similarity or differences in preferences across sample subgroups.

@@

Researchers and consumers of conjoints interested in describing levels of respondent favorability toward profiles with varying features can avoid the inferential errors that accompany conditional AMCEs by focusing attention on (subgroup) marginal means, differences between subgroup marginal means to infer subgroup differences in preferences toward particular features, and omnibus nested model comparisons to infer subgroup differences across many features. To demonstrate each of these three techniques we provide a complete example based upon \citeauthor{HainmuellerHopkinsYamamoto2014}'s analysis of their immigration conjoint by respondent enthnocentrism, which finds that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' \citep[22]{HainmuellerHopkinsYamamoto2014}. First, we show how different reference categories could have led to distinctly different conditional AMCEs and, therefore, interpretations of subgroup preference similarity. Second, we show how differences in marginal means clearly convey the similarity of these two subgroups without any sensitivity to reference category. Finally, we show how tested model comparisons would have provided \citeauthor{HainmuellerHopkinsYamamoto2014} with a statistic test of the claimed similarity in levels of support between these two respondent subgroups.

@@

<<hainmueller_subgroup_example_plot, dependson=c("data_hainmueller_immigration", "hainmueller_subgroup_example"), fig.width=8, fig.height=6, fig.cap="Comparison of AMCEs for Low- and High-Ethnocentrism Respondents Using Two Alternative Reference Categories Choices for Three Features from Hainmueller et al.'s (2014) Immigration Experiment", message=FALSE>>=
plot(
  subset(
    amce_ref_example_merged,
    feature %in% c("Education", "CountryOfOrigin", "Job")
  ),
  group = "ethnocentrism_split", 
  feature_headers = FALSE, 
  legend_title = "Ethnocentrism", 
  vline = 0
) + 
  scale_colour_manual(
    "Ethnocentrism", limits = c("high", "low"), values = c("Black", "Gray")
  ) +
  facet_grid(
    rows = vars(feature), 
    cols = vars(dataset), 
    scales = "free_y", 
    space = "free_y", 
    labeller = function(x) label_value(x, multi_line = FALSE)
  ) +
  theme(
    strip.background = element_rect(fill="white", colour="white"),
    strip.text.x = element_text(size = 8),
    strip.text.y = element_blank()
  )
@

To begin, consider the left and right facets of Figure \ref{fig:hainmueller_subgroup_example_plot}, which shows estimated subgroup AMCEs for three features from the immigration study. In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in levels of support between the two subgroups thus distorting the size of differences at all other levels. In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.

@@

<<hainmueller_mm_diffs, dependson=c("data_hainmueller_immigration"), fig.height = 5, fig.width=8, fig.cap="Differences in Conditional Marginal Means, by Ethnocentrism, for Three Features From Hainmueller et al.'s (2014) Immigration Experiment", message=FALSE>>=
mm_by_ethnocentrism <- cj(
  subset(hainmueller_immigration, !is.na(ethnocentrism_split)),
  ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry,
  id = ~ CaseID,
  estimate = "mm_diff",
  by = ~ ethnocentrism_split
)
plot(
  subset(
    mm_by_ethnocentrism,
    feature %in% c("Country of Origin", "Job", "Education")
  ), 
  vline = 0, 
  xlim = c(-0.3,0.3), 
  xlab = "Estimated Difference in Marginal Means"
) +
  scale_colour_manual("feature", values = rep("Black", 9)) +
  ggplot2::theme(legend.position = "none")
@

@@

<<hainmueller_anovas, dependson=c("data_hainmueller_immigration"), eval=TRUE, echo=FALSE>>=
hainmueller_anova_education <- cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ Education, id = ~ CaseID, by = ~ ethnocentrism_split)
hainmueller_anova_country <- cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, by = ~ ethnocentrism_split)
hainmueller_anova_job <- cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ Job, id = ~ CaseID, by = ~ ethnocentrism_split)
hainmueller_anova_all <- cj_anova(subset(hainmueller_immigration, !is.na(ethnocentrism_split)), ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry + Education:Job + CountryOfOrigin:ReasonForApplication, id = ~ CaseID, by = ~ ethnocentrism_split)
@

For the education feature, the resulting F-test for the model comparison in this case again gives us little reason to believe there are subgroup differences: \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_education$Df[2], hainmueller_anova_education[["Resid. Df"]][1], hainmueller_anova_education$F[2], hainmueller_anova_education$"Pr(>F)"[2])}. We could repeat such pairwise comparisons or omnibus comparisons for each feature in the design --- for country of origin (\Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_country$Df[2], hainmueller_anova_country[["Resid. Df"]][1], hainmueller_anova_country$F[2], hainmueller_anova_country$"Pr(>F)"[2])}) or job (\Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_job$Df[2], hainmueller_anova_job[["Resid. Df"]][1], hainmueller_anova_job$F[2], hainmueller_anova_job$"Pr(>F)"[2])}) --- or for all features as a whole (\Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", hainmueller_anova_all$Df[2], hainmueller_anova_all[["Resid. Df"]][1], hainmueller_anova_all$F[2], hainmueller_anova_all$"Pr(>F)"[2])}).

This visual display in Figure \ref{fig:hainmueller_mm_diffs} and these statistical tests make clear what could not be directly inferred from conditional AMCEs alone: there are indeed no sizeable and only a few statistically apparent differences in preferences between the two groups.

@@

This kind of nested model comparison test can also be used to assess heterogeneity across conjoint features \citep[see also][]{EgamiImai2018}. For example, \citet{TeeleKallaRosenbluth2018} report just such a test for how effects of features other than candidate sex may differ between male and female candidates, finding no such heterogeneity (8--9). Fortunately, the original analysis accurately detected an absence of subgroup differences, yet a subtly different set of analytic decisions about reference categories (as shown in Figure \ref{fig:hainmueller_subgroup_example_plot}) could have led to quite different inferences. As an example, \citet{BechtelScheve2013} argue that their conjoint results show ``individuals in all four countries [Germany, France, United States, United Kingdom] largely agree on which dimensions are important and to what extent'' \citep[13765]{BechtelScheve2013}, but a nested model comparison shows the countries do differ in their preferences \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", bechtel_anova_country$Df[2], bechtel_anova_country[["Resid. Df"]][1], bechtel_anova_country$F[2], bechtel_anova_country$"Pr(>F)"[2])}. This cross-country variation is largely driven by differences in sensitivity to monthly household costs feature, \Sexpr{sprintf("F(%d, %d)=%0.2f, $p\\leq%0.2f$", bechtel_anova_country_cost$Df[2], bechtel_anova_country_cost[["Resid. Df"]][1], bechtel_anova_country_cost$F[2], bechtel_anova_country_cost$"Pr(>F)"[2])}, with the United Kingdom and United States being more cost sensitive than Germany and France. Visual comparisons of conditional AMCEs can sometimes provide accurate insights into subgroup differences in preferences (as in the \citeauthor{HainmuellerHopkinsYamamoto2014} case), but ulimately there is no guarantee that they do in any particular analysis.

@@

This article has identified several challenges related to the analysis and reporting of conjoint experimental designs, particularly analyses of subgroup differences. We suggest that conjoint analyses should report not only average marginal component effects (AMCEs) but also descriptive quantities about levels of favorability that better convey underlying preferences over profile features and better convey subgroup differences in those preferences. Marginal means contain all of the information provided by AMCEs and more. Consequently, our intention here is not to substantively undermine any previous set of results, but instead to urge researchers moving forward to demonstrate considerable caution in how they design, analyze, and present the results of these types of descriptive experiments and how they test for differences in preferences between subgroups.

We have relatively straightforward and hopefully uncontroversial advice for how analysts of conjoint experiments should proceed:

@@

The popularity of conjoint analyses in recent years highlights the power of the design and the important contributions made by \citet{HainmuellerHopkinsYamamoto2014} in providing a novel causal interpretation of these fully randomized factorial designs. Yet with new tools always come new challenges. The now-common practice of descriptively interpreting conjoints requires more caution than is immediately obvious.

To facilitate improved analysis and, especially, to provide easy-to-use tools for calculating marginal means and performing reference category selection diagnostics, we provide software called \textbf{cregg} \citep{Leeper2018cregg} available from the Comprehensive R Archive Network. Additionally, this manuscript is written as a reproducible knitr document \citep{Xie2015} that contains complete code examples that will perform all analyses and visualization used throughout this article. With these resources in-hand, researchers should be well-equipped to analyze subgroup preferences in conjoint designs without running into the analytic challenges discussed here.

@@

\subsection{Replication using AMCEs}

<<hainmueller_immigration_amce_appendix, dependson=c("data_hainmueller_immigration"), fig.height=8, fig.width=8>>=
p1 <- plot(
  cregg::cj(
     hainmueller_immigration, 
     ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry + Education:Job + CountryOfOrigin:ReasonForApplication,
     id = ~ CaseID
  ), vline = 0
) + 
  ggplot2::scale_x_continuous(
    limits = c(-0.4, 0.4), 
    breaks = c(-0.4, -0.3, -0.2, -0.1, 0.0, 0.1, 0.2, 0.3, 0.4)
  ) + 
  ggplot2::geom_text(
    aes(label = ifelse(is.na(std.error), "", sprintf("%0.2f (%0.2f)", estimate, std.error))),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
 ) + 
 theme(legend.position="none")
p1
@

@@

\subsection{Replication using MMs}

<<hainmueller_immigration_mm_appendix, dependson=c("data_hainmueller_immigration"), fig.height=8, fig.width=8>>=
p2 <- plot(
  cregg::cj(
     hainmueller_immigration, 
     ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry,
     id = ~ CaseID,
     estimate = "mm"
  ), vline = 0.5
) + 
  ggplot2::scale_x_continuous(
    limits = c(0.1, 0.9), 
    breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
  ) + 
  ggplot2::geom_text(
    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
  ) + 
  theme(legend.position="none")
p2
@

@@

<<tkr_subgroup_example_plot, dependson=c("data_tkr", "tkr_subgroup_example"), fig.width=10, fig.height=10, fig.caption="Alternative Reference Categories Features in Teele et al. (2018) Candidate Experiment">>=
plot(
  amce_ref_tkr_merged, 
  group = "PartyID", 
  feature_headers = FALSE, 
  legend_title = "Party Identification", 
  vline = 0
) + 
  facet_grid(
    rows = vars(feature), 
    cols = vars(dataset), 
    scales = "free_y", 
    space = "free_y", 
    labeller = function(x) label_value(x, multi_line = FALSE)
  ) +
  theme(
      strip.background = element_rect(fill="white", colour="white"),
      strip.text.x = element_text(size = 8),
      strip.text.y = element_blank()
    )
@

@@

%\clearpage

%\subsection{Numerical Results: AMCEs}

@@

%\clearpage

%\subsection{Numerical Results: MMs}

@@

%\clearpage

@@

\subsection{Subgroup Analysis using MMs: Environmentalism}

@@

<<bechtel_reciprocity_reference, fig.height=5, fig.width=7>>=
# ``Individuals who pretreatment exhibit reciprocal behavior [...] are almost twice as sensitive to both the number of countries participating and the proportion of emissions represented than individuals who do not'' (13768). This sensitivity is accurately stated but the use of conditional AMCEs implies that the subgroup difference is due to differences in favorability toward agreements involving 20 countries and differing opinions over agreements with 80 or 160 countries, while in reality the differences lie in 20-country and 160-country agreements and the groups do not differ in their favorability toward 80-country agreements at all. 
plot(cj(bechtel, choice_cj ~ ctries_cj + emissions_cj, weights = ~ weight, id = ~ ID, estimate = "mm", by = ~ reciprocity), group = "BY", vline = 0.5)
@
